---
title: "Homework 1 -- QTM 151"
author: "Anna Choi"
output: html_document
---

```{r}
# Warming up
library(tidyverse)
```

## Homework 1

**1.** Load the `dat1.csv` and the `dat2.csv` from the class [GitHub page](https://github.com/umbertomig/qtm151). Use the function `read.csv` (not `read_csv`!).

```{r}
# Loading 'dat1' dataset
dat1 <- read.csv('https://raw.githubusercontent.com/umbertomig/qtm151/main/datasets/dat1.csv')
# Loading 'dat2' dataset
dat2 <- read.csv('https://raw.githubusercontent.com/umbertomig/qtm151/main/datasets/dat2.csv')
```

The datasets have information about airports. The first dataset (`dat1`), has info about names, time zones, etc. The second dataset (`dat2`) has info about the airports' latitudes, longitudes, and altitudes. We want to merge this information.

**2**. Using the `dplyr` function `inner_join`, join both datasets. Check the results using the function `summary`. After joining the datasets, how much missing data is there in the latitude variable?

```{r}
inner_join(dat1, dat2, by = "faa")

summary(dat2)
summary(inner_join(dat1, dat2))

# There is no missing data in the latitude variable.
```

**3**. Display all the cases, for each variable, in sequence.

```{r}
dat3 <- dat2[1:3,]

for(i in 1:nrow(dat3)){
  for(j in 1:ncol(dat3)){
    cat(dat3[i,j])
}}
```

**4**. The common variable in both datasets is `faa`, which is the Federal Aviation Administration code for the airport. Extract this variable, and use a `for` loop to print each value. Use `print` to print the data row by row.

```{r}
# Printing the first five rows of 'faa' variable
for(i in dat1[1:5, 'faa']){
  print(i)
}
```

**5**. Using the function `subset`, extract the lines in the left that match with the third value of `dat1[,'faa']` in both datasets.

```{r}
subset(dat1, dat1[,'faa'] == dat1[3,'faa'])
```

**6**. Using a for-loop on the content of the `faa` variable, extract and print (with `print`) the first five lines of `dat1`.

```{r}
for(i in 1:5){
  print(dat1[i, 1:5,])
}
```

**7**. Extract the row associated with `faa = 06A` in `dat1` and `dat2`. Join the two rows horizontally (binding the columns) by using the command `cbind`. Then, note that it joins `faa` twice. Remove one of the entries.

```{r}
cbind(dat1[2,], dat2[2, setdiff(names(dat2), 'faa')])
```

**8**. Extract the row associated with `faa = 04G` and the row associated with `faa = 06A` from `dat1` and `dat2`. Join the rows for each `faa` code horizontally, and then join both results vertically. Make sure that the `faa` variable shows up only once.

```{r}
rbind(cbind(dat1[1,], dat2[1, setdiff(names(dat2), 'faa')]), cbind(dat1[2,], dat2[2, setdiff(names(dat2), 'faa')]))
```

**9**. Using for-loops, automate the process for all the `faa` codes. Save the result in a blank dataset `aux`.

```{r}
aux <- data.frame()
for(i in 1:nrow(dat1)){
    aux <- rbind(cbind(dat1[1:i,], dat2[1:i, setdiff(names(dat2), 'faa')]))
}

aux
```

**10**. Build a function `my_join`, that receives a left-dataset, a right-dataset, and a `by = 'variable_name'` to index the matches.

```{r}
my_join <- function(left_dataset, right_dataset, by = 'variable name'){
  aux <- data.frame()
  for(i in 1:nrow(left_dataset)){
    aux <- rbind(cbind(left_dataset[1:i,], right_dataset[1:i, setdiff(names(right_dataset), by)]))
}
  return(aux)
}
```

Which function is faster: `inner_join` or your own `my_join`? Compare using the question in [here](https://stackoverflow.com/questions/6262203/measuring-function-execution-time-in-r).

```{r}
system.time(inner_join(dat1, dat2, by = 'faa'))
system.time(my_join(dat1, dat2, by = 'faa'))

# 'inner_join' is faster.
```