---
title: "Homework 2 - qplot"
author: "Anna Choi"
output: html_document
---

Please use `qplot` instead of `ggplot`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
data(diamonds)
library(plotly)
library(gapminder)
set.seed(123)
```

**Q1**: (2 points) Make a small random subset of diamonds and name it as `dsmall`. You can use the function `sample` or any other function of your choice.

```{r}
dsmall <- diamonds[sample(1:nrow(diamonds), 100, replace = FALSE),]
```

**Q2**: (2 points) Show the distribution of carat with a histogram, set binwidth to 0.1 and limits for the x-axis from 0
to 3.

```{r}
qplot(carat, geom = "histogram", data = diamonds,
      binwidth = 0.1, xlim = c(0, 3))

# The histogram is skewed to the right.
```

**Q3**: (2 points) Show the distribution of carat with a *density plot*, set the color to the variable `color`.

```{r}
qplot(carat, geom = "density", data = diamonds,
      color = color)
```

**Q4**: (2 points) Produce a scatter-plot showing the relationship between *carat* and *price*, set point shape to the
variable cut, set point transparency to 0.1, and describe the trend of the scatter-plot.

```{r}
qplot(diamonds$carat, diamonds$price, geom = "point",
      shape = diamonds$cut, alpha = I(0.1))

# There is a positive, non-linear association between the two variables carat and price. The price tends to increase as the carat increases, and the points do not cluster along a straight line. There appear to be some potential outliers in the subset of data. 
```

**Q5**: (2 points) Make another scatter-plot between *carat* and *price*, add jitters to points, set point transparency to 0.1, apply log transformation to the x and y axes variables, and add a smooth line to the plot, then describe the trend of the scatter-plot.

```{r}
qplot(diamonds$carat, diamonds$price, geom = c("point", "smooth", "jitter"),
      shape = diamonds$cut, alpha = I(0.1), aes(log(diamonds$carat), log(diamonds$price)))

# There is a positive, linear association between the two variables carat and price. The price tends to increase as the carat increases, and the points cluster along a straight line. 
```